Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/old_paper.tex
new command in old paper
latest

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage {graphicx}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

\newcommand{\tol}{Tololo 1214-277}
\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\newcommand{\apj}{ApJ}  
\newcommand{\jcap}{JCAP}  
\newcommand{\apjs}{ApJS}  
\newcommand{\pasa}{PASA}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}

@@

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric \lya\ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

\begin{keywords}
Methods: data analysis - numerical 
\end{keywords}

@@

Primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process. 
Over fifty years ago \citep{PartridgePeebles} it was realized that
young galaxies could be detected through a strong \lya\ line
emission.

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya\ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya\ emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos \cite{2016ApJ...828....5M}.

The \lya\ emission line is not exclusive of distant galaxies. 
There are local Universe surveys that target \lya\ emission in nearby
dwarf star forming galaxies.
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as morphology, dust attenuation, neutral hydrogen contents and
ionization state. (see \citep{Hayes15} and references therein for a review.)

However, the physical interpretation of \lya\ observations is
not straightforward \citep{LARS,2015ApJ...805...14R}. 
This is due to the resonant nature of the \lya\ line. 
A \lya\ photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are very few analytically tools available to interpret the
emerging \lya\ line
\cite{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
They are applicable only in very few cases of highly symmetrical
conditions, which are hardly met in real astrophysical systems.
For these reasons the interpretation of \lya\ observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

\tol\ is a compact star forming dwarf galaxy that presents a
strong \lya\ emission \citep{Thuan97} with two puzzling 
features: the line is symmetric, single peaked and wide around the
line's center.
Usually the \lya\ line has an asymmetric single or double peak. 
These two special features in \tol\ cannot be explained quantitatively
with conventional shell models
\citep{Mas-Hesse09,2015A&A...578A...7V,2015ApJ...812..123G}.

This kind of profile also raises the question whether some high redshift
LAEs have asymmetric lines because the blue half was truncated by the
intergalactic medium \citep{2007MNRAS.377.1175D}. 
In this case the \lya\ radiation could emerge as a low surface
brightness glow, which may be connected to \lya\ halos, while also
influencing the way LAEs can be used as a probe of reionization
\citep{2014PASA...31...40D}.

Here we show how the \tol's \lya\ profile can be explained
either by  or the recently developed class of complex multiphase models 
\citep{Gronke2016} or by a simple rotation model
\citep{GaravitoCamargo2014}. 
The models we use correspond to simplified geometrical configurations
to allow a deep exploration of parameter space and gain, for the first time,
some physical insight into the \tol's kinematic properties.

We review first the observational characteristics of
\tol, then we summarize the main features in the multiphase and
rotation models to explain how we fit their free parameters 
to the \tol's \lya\ line shape.
We use the results to interpret them in terms of the galaxy's
dynamical mass. 
We close by discussing the physical scenarios that open up by our
results and the additional observational information needed to clarify
the kinematic nature of \tol.

\section{Observations}
\tol's basic observational characteristics are summarized in Table \ref{obstable}.
Its receding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
km s$^{-1}$ Mpc$^{-1}$.)

The observed flux for the \lya\ line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
\citep{Izotov04} which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1.
The \lya\ flux values correspond to luminosities of
$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
translates  into a star formation rate of $2.0$ M$_{\odot}$ yr$^{-1}$
using a standard conversion factor between luminosity and star
formation rate of $9.1\times 10^{-43}$ $L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
The absolute magnitude in the $V$ band translates into a luminosity of
$8.9\times 10^{8}$ L$_{\odot}$.
% using http://tomdwelly.com/tools_fluxtolum.php
Comparing this ratio with the theoretical expectation from case B
recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
fraction of $20$\% for \lya\ radiation.
The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
L$_{\odot}$ as measured by GALEX, without any correction by extinction
and following the empirical relation by \cite{Kennicutt98}, this
corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
yr$^{-1}$. Its metallicity is $\sim Z_{\odot}/24$ as derived from
optical spectroscopy \citep{Izotov04}.

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\citep{2008ApJ...678..804E}.
Using a conversion between fluxes and
stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
process \citep{2012AJ....143..139E}.

We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
from the surface intensity profiles reported by \citep{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.

There is an upper limit for the  
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\citep{pustilnikmartin07}.

\begin{table}
\begin{center}
\begin{tabular}{lc}\hline
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
\lya\ Equivalent Width (\AA) & $70$\\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \citep{Thuan97}\label{obstable}} 
\end{table}

\begin{figure*}
\begin{center}
\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.
The observational points corresponds to the data as shown in
\citep{mashesse03}.}   
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
  and its corresponding physical parameters.
  Only the  25 models with the lowest $\chi^2$ are included.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
\caption{Results from the Markov Chain Monte Carlo computation for
    the rotation model. The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure*}

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$, which also include information about the spatial
distribution and thermal state of the clumps and the intraclump
medium.

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range,
based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented by
\citet{Gronke2016}.

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}

where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the $\chi^2$ gap in those $25$ models is close to
$\Delta\chi^2 = 3000$, the lowest $\chi^2$ being close to
$\chi^2_{min}=1200$.
To have a sense of scale, the total number of degrees of freedom is
$104$.

Then we perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
this parameter does influence the $\chi^2$ fit, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

The best values for the influential parameters correspond to
the values that produce the minimum
$\chi^2$.
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.   
%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
%$P_{\rm cl}$

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage[draft]{hyperref}
%Non reposionated tables

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\tol}{Tololo 1214-277}
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
%\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}

\newcommand{\mg}[1]{\textcolor{blue}{\bf MG: \textit{#1}}}

@@

\begin{abstract}

Star-forming Compact Dwarf Galaxies (CDGs) 
resemble the expected pristine conditions of the first galaxies in the
Universe and are the best systems to test models on primordial galaxy
formation and evolution. 
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya emission line that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya spectrum can be explained
assuming either of these kinematic conditions.
The multiphase model requires a clump velocity dispersion of
at least \sigmaclump\ with outflows of \inftyclump\, while the
bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
We argue that the multiphase model has more chances to be correct.
The clump velocity dispersion implies a dynamical mass of at least $2\times
10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
explained if \tol\ is hosted by a dark matter halo of at least
$6\times 10^{11}$ M$_{\odot}$.
If future kinematic maps of \tol\ confirm the velocities suggested by the
multiphase model, it would provide additional support to expect this
condition to be present  in primordial \lya emitting galaxies.  
\end{abstract}

\begin{keywords}
galaxies: dwarf --- galaxies: individual:\tol\ --- radiative transfer --- Methods: numerical 
\end{keywords}

@@

Primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process. 
Over fifty years ago it was realized that young galaxies could be
detected through a strong \lya line emission \citep{PartridgePeebles}.

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya emission line gives confirmation of
the distance to a galaxy and provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos
\citep{2004AJ....128.2073H,2007ApJ...671..278G,2007ApJ...668...15K,2008MNRAS.391.1589O,2010MNRAS.409..184P,2013MNRAS.431.1777G,2016ApJ...828....5M}.

The \lya emission line is not exclusive of distant galaxies. 
There are local Universe surveys that target \lya emission in nearby
dwarf star forming galaxies.
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as galaxy morphology, dust attenuation, neutral hydrogen contents and
ionization state. See \cite{Hayes15} and references therein for a review.

However, the physical interpretation of \lya observations is
not straightforward \citep{LARS,2015ApJ...805...14R}. 
This is due to the resonant nature of the \lya line. 
A \lya photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are few analytical tools available to interpret the
emerging \lya line
\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
They are applicable only in cases of highly symmetrical
conditions of the gaseous hydrogen distribution in the galaxy model,
which are hardly met in real astrophysical systems. 
For these reasons the interpretation of \lya observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

Observed \lya line profiles usually present a single peak shifted
redwards from the line's center. 
Sometimes a double peak is present but the asymmetry persists with 
the peak on the red side being stronger \citep[e.g.][]{2010ApJ...717..289S,Erb14,Trainor16}. 
This can be explained as the results of multiple \lya photon
scatterings through an outflowing shell of neutral Hydrogen
\citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.

\tol\ is a compact star forming dwarf galaxy that presents a
strong \lya emission with puzzling 
features: the line is highly symmetric, single peaked and broad 
\citep{Thuan97}.
This kind of profile also raises the question whether some high
redshift LAEs have asymmetric lines because the blue half was
truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
In this case the \lya radiation could emerge as a low surface
brightness glow, which may be connected to \lya halos, while also
influencing the way LAEs can be used as a probe of reionization
\citep[see the review by][and references therein]{2014PASA...31...40D}.

Attempts to explain the atypical \lya features in \tol\ with
conventional models based on a expanding shell have not been successful
so far \citep{mashesse03,2015A&A...578A...7V}. 
This justifies a new study using two new physically motivated
situations: a multiphase outflowing interstellar medium and bulk rotation for a
galaxy without outflows.

The main motivation for the outflowing multiphase model \citep[as presented
in][]{Gronke2016} is that some dwarf galaxies are expected to
present outflows.  
Observationally, outflows have been detected in few local dwarf galaxies
\citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
Besides, clumpy multiphase outflows are capable to explain \lya features around
star-forming galaxies
\citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
In addition, due to the cooling properties of gas multiphase media are expected
in a range of astrophysical systems \citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.

The motivation for the rotation without outflows (as presented in
\cite{GaravitoCamargo2014}) is that dwarf galaxies show coherent
rotation features  \citep{2009A&A...493..871S} and it is expected that
some of them have high neutral gas contents with long quiescent phases
without high gas outflows triggered by supernova activity
\citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.

The models we use correspond to simplified geometrical configurations.
This allows us to perform a deep exploration of parameter space and
gain some physical insight into \tol's kinematic properties.
In this paper we show, for the first time in the literature, that \tol's
\lya profile can be explicitly modeled by either of these two
models.

\mg{I would remove the next paragraph as this seems clear and not necessary to start with an ``apology''.}
We do not claim that our findings discard the existence of different
undiscovered models that could reproduce the observed features in \tol.
More involved models with multiple kinematic components can
in principle also be successful.
We focus on presenting two simple and successful models that
manage, for the first time, to account for \tol's \lya line main
features.

In the next section we review the observational characteristics of
\tol, then we summarize the main features in the multiphase and
rotation models to explain how we fit their free parameters 
to the \tol's \lya line shape.
We use the results to interpret them in terms of the galaxy's
dynamical mass and argue why the multiphase model should be preferred
over the rotation model.
We close by discussing the additional observational information needed
to clarify the kinematic nature of \tol.

\section{Observations}

\begin{table}
\begin{center}
\begin{tabular}{lr}\hline
$\alpha$(2000)& 12h17min17.1s\\
$\delta$(2000)& -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
Redshift & $0.026\pm0.001$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of \tol\ 
  \citep{Thuan97}\label{obstable}} 
\end{table}

\begin{table*}
  \centering
\begin{tabular}{l|lrrl}
\hline
  Parameter  & Description & Fiducial value & Allowed range & Units \\ \hline\hline
$v_{\infty,\,{\rm cl}}$ & Radial cloud velocity & $100.0$ & [$0.0$, $800.0$] & $\,{\rm km\,s}^{-1}$ \\
$\sigma_{\rm {\rm cl}}$ & Random cloud motion &$40.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$P_{\rm {\rm cl}}$ & Probability to be emitted in cloud & $0.35$ & [$0.0$, $1.0$] &  \\
$r_{\rm {\rm cl}}$ & Cloud radius & $100.0$ & [$30.0$, $200.0$] & $\,{\rm pc}$ \\
$H_{\rm em}$ & Emission scale radius & $1000.0$ & [$500.0$, $3.0\times 10^{3}$] & $\,{\rm pc}$ \\
$f_{\rm {\rm cl}}$ & Cloud covering factor & $3.5$ & [$0.8$, $8.0$] &  \\
$T_{\rm {\rm ICM}}$${}^{\dagger}$ & Temperature of ICM & $10^{6}$ & [$3.0\times 10^{5}$, $5.0\times 10^{7}$] & $\,{\rm K}$ \\
$n_{\rm HI,\,{\rm ICM}}$${}^{\dagger}$ & \HI number density in ICM & $5.0\times 10^{-8}$ & [$10^{-12}$, $10^{-6}$] & $\,{\rm cm}^{-3}$ \\
$\sigma_{\rm i}$ & Width of emission profile & $50.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$T_{\rm {\rm cl}}$${}^{\dagger}$ & Temperature in clouds & $10^{4}$ & [$5.0\times 10^{3}$, $5.0\times 10^{4}$] & $\,{\rm K}$ \\
$\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps &
  $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] &
  $\,\cm^{2}$ \\
$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance &
  $0.01$ & [$10^{-4}$, $0.1$] & \\
$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in
  clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
\hline
\end{tabular}
  \caption{Overview of the parameters in the multiphase model and its fiducial
    values. Variables marked with ${}^{\dagger}$ were drawn in
    log-space. Table reproduced from \citet{Gronke2016}.}
  \label{tab:models}
\end{table*}

\tol's basic observational characteristics are summarized in Table \ref{obstable}.
Its receding velocity is $7785\pm 50$km s$^{-1}$ translates
into a distance of $106.6$ Mpc, using a Hubble constant value of $H_{0}$=73
km s$^{-1}$ Mpc$^{-1}$.

Archival Chandra X-ray data\footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol. 
This lack of detection motivates our assumption that \lya emission is
powered by star formation only.

The observed flux for the \lya line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1 \citep{Izotov04}.
Comparing the \lya/H$\beta$ ratio with the theoretical
expectation from case B recombination of $23.3$ \citep{Hummer1987} one
can estimate an escape fraction of $20$\% for \lya radiation.

The \lya flux values correspond to a luminosity of
$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
translates  into a lower bound for the star formation rate of $2.0$
M$_{\odot}$ yr$^{-1}$ after using a standard conversion factor between
luminosity and star formation rate of $9.1\times 10^{-43}$
$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ 
without any
correction by extinction
\citep{Kennicutt98}.

The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
L$_{\odot}$ as measured by GALEX. Without any correction by extinction
and following the empirical relation by \cite{Kennicutt98}, this
corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
yr$^{-1}$. 
The absolute magnitude in the $V$ band translates into a luminosity of
$8.9\times 10^{8}$ L$_{\odot}$.  
Its metallicity is $\sim Z_{\odot}/24$ as derived from
optical spectroscopy \citep{Izotov04}. 
% using http://tomdwelly.com/tools_fluxtolum.php
%

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\citep{2008ApJ...678..804E}.
Using the conversion between fluxes and
stellar mass, $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$,  calibrated on the Large Magellanic Cloud 
and  where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
process \citep{2012AJ....143..139E}.  
There is an upper limit for the  $21$ cm line integrated flux of $<0.10$
Jy km s$^{-1}$  which translates into a upper limit for the neutral
Hydrogen mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\citep{pustilnikmartin07}.

We compute the projected half-light radius to be $R_s=1.5\pm0.1$ kpc 
from the surface brightness profiles reported by \cite{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-light radius of $r_s=3R_s/2=2.25$ kpc.
Imaging observations by \cite{2001AJ....121..169F} show that \tol\ is
an isolated field galaxy not belonging to a group or cluster.

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium \citep{Gronke2016}. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.
We do not explore inflowing clumps given the slight line asymmetry
redwards to the line center (see the dots in Figure \ref{fig:results})
and thus set $v_{\infty,\,{\rm cl}}>0$.
The parameter description list is in Table \ref{tab:models}.

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range,
based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the spectral features as well as
more details on the radiative transfer are presented by
\citet{Gronke2016}.

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a 
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models as

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}
%
where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.
As we do not have an analytic expression for $\hat{f}$;
we obtain $\hat{f}$ from the binned results of the Monte Carlo radiative transfer simulations.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{\mathrm{min}}=1200$.

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
this parameter does influence the $\chi^2$ result, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

We finally compute the best values for the influential parameters as
the values that produce the minimum $\chi^2$.  
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.

\begin{figure*}
\begin{center}
\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and highly symmetric \lya emission of \tol.
  Dots correspond to the observational data \citep{mashesse03}. 
The thick red and thin blue curves represent our best fit
to the data using the full radiative transfer simulation with a
rotation and multiphase model, respectively. 
These two different models are able to reproduce the main morphological
features of \tol's \lya line emission.\label{fig:results}}
\end{center}
\end{figure*}
